Compute Servers for Teaching Big Data

### 2025-01-28 paper.tex
revise abstract

\usepackage{geometry}
\geometry{margin=1in}

@@

    It's a useful skill for students in data science to analyze and process large data sets located on remote servers.
    To teach students these skills, we need to provide them with an authentic experience of logging in to a remote server and using it to answer questions based on a real world, large data set.
    We offer practical suggestions to the instructor interested in using servers to teach data analysis, and share our experience using a variety of server options to teach this content, both with and without dedicated institutional support.
    We compare and contrast different options including public and private cloud services, and personal physical machines.
    Finally, we suggest a more sustainable sharing model that will allow more instructors to teach such classes without the overhead of having to manage their own server.

>>>>

\usepackage{geometry}
%\geometry{margin=1in}

\usepackage{setspace}
\doublespacing

@@

    We compare and contrast different server options for providing undergraduate students with an authentic experience analyzing large, real world data sets located on powerful remote servers.
These server options include institutionally supported academic computers, commercial cloud services, public cloud services, and personal physical machines.
% TODO: Align these options with the sections
We briefly describe the course, and offer suggestions on when to choose which server option, based on the background of the instructor and the level of institutional support.
Looking to the future, we suggest requirements for a broadly shared educational compute service that will allow more instructors to teach similar classes without the overhead of having to manage and administer their own server.
